Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-29 poster/main.tex
minor poster rewording

Parallel linear recurrence enables rapid learning on extremely long sequences at small
minibatch sizes. A significant portion of deep learning's current success can be
attributed to highly efficient matrix multiplication and convolution kernels.
We hope that parallel linear recurrence can join these algorithms and
be to large scale sequence
modelling what fast convolution algorithms are to image recognition.

>>>>

Parallel linear recurrence enables rapid learning on extremely long sequences at small
minibatch sizes. A significant portion of deep learning's current success can be
attributed to highly efficient matrix multiplication and convolution kernels.
We hope that parallel linear recurrence can join these algorithms and
be to large scale sequence
modelling what fast convolution is to image recognition.
